Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
nouns to verbs

\gls{MSR} modeling efforts describe steady-state and
transient behavior. Krepel et. al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. DYN3D-MSR was compared against
experimental \gls{MSRE} data and was then used to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three-dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze normal 
\gls{MSRE} operation as well as channel-blocking-incident
transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics \cite{cammi_multi-physics_2011}. Advances in that work included
solution of the fuel salt velocity field, use of heterogeneous group constants
in fuel and moderator regions, and employment of a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.

>>>>

\gls{MSR} modeling efforts describe steady-state and
transient behavior. Krepel et. al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. DYN3D-MSR was compared against
experimental \gls{MSRE} data and was then used to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three-dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze normal 
\gls{MSRE} operation as well as channel-blocking-incident
transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
fuel salt velocity field, used heterogeneous group constants
in fuel and moderator regions, and employed a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.
